On the presentation of orthogonal groups over polynomial rings

### 2019-05-24 dl-paper.tex
Switched to biber, restored correct operation of live preview, fixed some warnings

\documentclass[oneside, 8pt]{amsart}
\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
\usepackage[breaklinks=true]{hyperref}
\usepackage[hyperref=true, backend=bibtex, firstinits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
\usepackage[capitalize]{cleveref}
\usepackage[matrix,arrow,curve]{xy}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage[notref,notcite]{showkeys}

@@

\DeclareMathOperator{\Ker}{Ker}
\DeclareMathOperator{\Img}{Im}
\DeclareMathOperator{\St}{St}
\DeclareMathOperator{\G}{G}
\DeclareMathOperator{\E}{E}
\DeclareMathOperator{\HH}{H}
\DeclareMathOperator{\K}{K}
\DeclareMathOperator{\GW}{GW}
\DeclareMathOperator{\colim}{colim}
\newcommand{\inv}{^{-1}}

@@

\subsection{Computation of the kernel of the map of evaluation at $0$.}
For a pair $(R, I)$ we denote by $\overline{\St}(\Phi, R, I)$ the image of the map $\mu$ from~\eqref{relSteinberg-def}, in particular, it is a normal subgroup of $\St(\Phi, R)$.
We also denote by $\St(\Phi, I)$ the subgroup of $\St(\Phi, R)$ generated as a group by root unipotents of level $I$.
It is clear that $\overline{\St}(\Phi, R, I)$ contains $\St(\Phi, I)$ and, in fact, is its normal closure.
We also denote by $\overline{H}(\Phi, R, I)$ the subgroup of $\overline{\St}(\Phi, R, I)$ generated by the semisimple root elements $h_\alpha(u)$ and symbols $\{u, v\}$, $u \in (1+I)^*$, $v \in R^*$, $\alpha\in \Phi$.

@@

\subsection{The subgroups $P_\alpha(0)$, $P_\alpha(*)$ and their properties.} 
Assume for a moment that $\Phi$ is an arbitrary root system and consider the following subsets of $\Phi$:
\begin{equation} \nonumber \begin{align}
   Z_+(\alpha) & = \{ \beta \in \Phi \mid \langle \alpha, \beta \rangle > 0 \}, \\
   Z_0(\alpha) & = \{ \beta \in \Phi \mid \alpha + \beta \not\in \Phi,\ \langle \alpha, \beta \rangle = 0 \}, \\
   Z(\alpha)   & = Z_0(\alpha) \sqcup Z_+(\alpha). \end{align} \end{equation}
Clearly, $Z_0(\alpha)$ (resp. $Z_+(\alpha)$) is a reductive (resp. special) subset of $\Phi$, moreover, in the simply-laced case the assumption $\alpha+\beta\not\in \Phi$ in the definition of $Z_0(\alpha)$ is superfluous, i.\,e. $Z_0(\alpha) = \{ \alpha\in\Phi \mid \alpha \perp \beta \}$
(cf.~\cite[Proposition~5.7]{St71}).

@@

For the rest of this subsection $\Phi$ is a simply-laced root system of rank $\geq 3$ and $\alpha$ is a root of $\Phi$.

@@

\subsection{The subgroups $K(\alpha, \beta)$ and their properties}
Throughout this subsection $\alpha, \beta$ denote a fixed pair of roots of $\Phi$ forming a sharp angle (i.\,e. $\langle \alpha, \beta \rangle = 1$). We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
\begin{df} Denote by $K(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the following elements:
 \begin{enumerate}
  \item $z_\gamma(Xf, \xi)$, for all $\gamma \in \Phi \setminus \Psi$;
  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$;
  \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
  \item $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$. \end{enumerate} \end{df}

@@

The next step of the proof is to pass from the set $V_0'$ to its quotient $V_0$ 
We allow multiplying the second component on the right by an element of $\mathrm{im}(\St(\Phi, A, M) \to \St(\Phi, A))$
 (this operation is well defined for $V'_0$).

\begin{multline}
 T_\alpha(bX^{-1}) T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim
T_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
 = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h',\ u(1 + am + bm) \right) \sim T_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right),\text{ since} \end{multline} 
 \begin{multline}
h' = h \cdot x_\alpha\left(-\frac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-\frac{bX^{-1}}{1 + \frac{bm}{1+am}}\right) = \\ = 
 h \cdot x_\alpha\left(- \frac{aX^{-1}}{1 + am} - \frac{bX^{-1}}{(1+am)(1 + am + bm)}\right) \cdot h^{-1}_\alpha(1+am) \sim  
  h \cdot x_\alpha\left(- \frac{(a+b)X^{-1}}{1 + am + bm}\right).
\end{multline}

If $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $\pi(g, h, u) \in P(\alpha, m) \cap P(\beta, m')$ then
$S_\alpha(a, \pi(g, h, u))\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \in P(\beta, \frac{m'}{1 + am})$
%($\beta = 2r$, $\alpha = 1r$, $\gamma = 12$, $\gamma = \alpha - \beta$)
\begin{multline}
 T_\beta(bX^{-1}) T_\alpha(aX^{-1}) \left(g, h, u\right) = 
 T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) ,\ u(1 + am)\right) \sim \\ 
 \sim T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-m'a),\ u(1 + am)\right) = \\
 = (x_\beta(bX^{-1}) x_\alpha(aX^{-1}) \cdot g, h', u(1 + am + bm')), \text{ where} \end{multline} 
 \begin{multline}
 h' = h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \cdot x_\beta\left(-\frac{bX^{-1}(1+am)}{1 + am + bm'}\right) \sim \\
    \sim h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha}\left(\frac{m'abX^{-1}(1+am)}{1 + am + bm'}\right) \cdot x_\beta\left(-\frac{bX^{-1}(1+am)}{1 + am + bm'}\right) = \\
 = h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am} + \frac{m'abX^{-1}}{(1+am)(1 + am + bm')}\right) \cdot x_\beta\left(-\frac{bX^{-1}(1+am)^{1 -\langle \beta, \alpha \rangle}}{1 + am + bm'}\right) \cdot h^{-1}_\alpha(1 + am) \sim \\
 \sim h \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\frac{bX^{-1}}{1 + am + bm'}\right).
\end{multline}
The latter expression is symmetric.
\begin{comment}
If $\alpha + \beta \in \Phi$, $\pi(g, h, u) \in P(\beta, m) \cap P(\alpha + \beta, m')$ then
\[x_\alpha(-a) \cdot S_\beta(-b, \pi(g, h, u)) h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm')) \in P\left(\beta, \frac{m + am'}{1-bm}\right)\]

($\alpha = 21$, $\beta = 1r$, $\alpha + \beta = 2r$)
($\alpha = 21$, $\beta = 13$, $\alpha + \beta = 23$)
\begin{multline}
\left(\begin{array}{ccc} 
 1 & 0 & -bX^{-1} \\
 0 & 1 & 0 \\
 0 & 0 & 1 
 \end{array}\right)
\left(\begin{array}{ccc} 
 1 & 0 & * \\
 0 & 1 & * \\
 mX & m'X & 1 
 \end{array}\right)
 \left(\begin{array}{ccc} 
 1 & 0 & \frac{bX^{-1}}{1 - bm} \\
 0 & 1 & 0 \\
 0 & 0 & 1 
 \end{array}\right) = 
 \left(\begin{array}{ccc} 
 1 - bm & -bm' & * \\
 0 & 1 & * \\
 mX & m'X & (1 - mb)^{-1} 
 \end{array}\right) = S_\beta(-b, g^+).
\end{multline}
\begin{multline}
\left(\begin{array}{ccc} 
 1 & 0 & 0 \\
 -a & 1 & 0 \\
 0 & 0 & 1 
 \end{array}\right)
 \left(\begin{array}{ccc} 
 1 - bm & - bm' & * \\
 0 & 1 & * \\
 mX & m'X & (1 - bm)^{-1} 
 \end{array}\right) = 
 \left(\begin{array}{ccc} 
 1 - bm & - bm' & * \\
 - a + abm & 1 + abm' & * \\
 mX & m'X & (1 - bm)^{-1} 
 \end{array}\right) = x_\alpha(-a) \cdot S_\beta(-b, g^+)
\end{multline}
\begin{multline}
 \left(\begin{array}{ccc} 
 1 - bm & - bm' & * \\
 - a + abm & 1 + abm' & * \\
 mX & m'X & (1 - bm)^{-1} 
 \end{array}\right)
 \left(\begin{array}{ccc} 
 (1  - bm)^{-1} & 0 & 0 \\
 0 & 1 & 0 \\
 0 & 0 & 1 - bm 
 \end{array}\right) \cdot \\ \cdot
\left(\begin{array}{ccc} 
 1 + abm' & 0 & 0 \\
 0 & (1 + abm')^{-1} & 0 \\
 0 & 0 & 1 
 \end{array}\right)
 \left(\begin{array}{ccc} 
 1 & 0 & 0 \\
 a(1 + abm') & 1 & 0 \\
 0 & 0 & 1 
 \end{array}\right) = \\
 = 
 \left(\begin{array}{ccc} 
 1 & - \frac{bm'}{1 + abm'} & * \\
 0 & 1 & * \\
 \frac{(m + m'a)X}{1 - bm} & \frac{m'X}{1 + abm'} & 1 
 \end{array}\right)
\end{multline}

There is still a mistake in the last implication :(
Perhaps one must replace $1 + abm'$ with $1 + ab N_{\alpha, \beta} m'$.

\begin{multline}
[T_\alpha(a), T_\beta(bX^{-1})] \left( g, h, u \right) =
 T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) \cdot g, h \cdot x_\beta\left(\frac{bX^{-1}}{1-bm}\right) , u (1 - bm) \right) \sim \\
 \sim T_\alpha(a) T_\beta(bX^{-1}) \left( x_\alpha(-a) \cdot x_\beta (-b X^{-1}) g, h \cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm')), u (1 - bm) \right) = \\
 = \left([x_\alpha(a), x_\beta(bX^{-1})] g, h', u (1 + abm')\right) \sim T_{\alpha}(N_{\alpha, \beta}abX^{-1})(g, h, u), \text{ since}\end{multline} 
 \begin{multline} h' = h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha}(a(1 + abm'))\cdot x_\beta\left(-\frac{b(1 - bm)X^{-1}}{1 + abm'}\right) \sim \\
 \sim  h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm')\cdot x_{\alpha + \beta}\left(-N_{\alpha, \beta}\cdot ab(1-bm)X^{-1}\right)\cdot x_\beta\left(-\frac{b(1 - bm)X^{-1}}{1 + abm'}\right) = \\
 = h\cdot x_\beta\left(\frac{b X^{-1}}{1-bm}\right) \cdot x_{\alpha + \beta}\left(-\frac{N_{\alpha, \beta} \cdot abX^{-1}}{1-abm'}\right)\cdot x_\beta\left(-\frac{bX^{-1}}{1 - bm}\right) \cdot h_{\beta}^{-1}(1-bm)\cdot h_{\alpha}^{-1}(1 + abm') \sim
 h\cdot x_{\alpha + \beta}\left(\frac{N_{\alpha, \beta} \cdot abX^{-1}}{1+abm'}\right).
\end{multline}

Full axioms
\begin{enumerate}
 \item (+) $P(\alpha, m)$ contains $\mathrm{K}_2(\Phi, R[t, t^{-1}])$ (or at least the subgroup generated by symbols $\{ X, - \}$ and Steinberg/Dennis--Stein symbols);
 \item (+) if $g \in P(\alpha, m)$ then $S_\alpha(a, g) \cdot h_\alpha^{-1}(1 + am) \in P(\alpha, \frac{m}{1 + am})$;
 %\item if $\alpha \perp \beta$ then $g \in P(\alpha, m) \cap P(\beta, m')$ implies $S_\alpha(a, g) \in P(\beta, m')$;
 \item (+) if $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $g \in P(\alpha, m) \cap P(\beta, m')$ then $S_\alpha(a, g)\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \in P(\beta, \frac{m'}{1 + am});$
 \item (+) If $\alpha + \beta \in \Phi$ and $g \in P(\alpha, m) \cap P(\alpha + \beta, m')$ then
 $x_\beta(b) \cdot S_\alpha(a, g) \cdot h_{\beta}^{-1}(1+am)\cdot h_{\alpha}^{-1}(1 + N_{\alpha, \beta}abm')\cdot x_{\alpha}(-b(1 + N_{\alpha, \beta}abm')) \in P(\alpha, \frac{m - bm'}{1+am}).$
\end{enumerate}

Restricted axioms:
\begin{enumerate}
 \item (+) $P(\alpha, 0)$ contains $\mathrm{K}_2(\Phi, R[t, t^{-1}])$ (or at least the subgroup generated by symbols $\{ X, - \}$ and Steinberg/Dennis--Stein symbols);
 \item (+) if $g \in P(\alpha, 0)$ then $S_\alpha(a, g) \in P_\alpha(\alpha, 0)$;
% \item if $\alpha \perp \beta$ then $g \in P(\alpha, 0) \cap P(\beta, 0)$ implies $S_\alpha(a, g) \in P(\beta, 0)$;
 \item (+) if $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $g \in P(\alpha, 0) \cap P(\beta, 0)$ then
$S_\alpha(a, g) \in P(\beta, 0);$
 \item (+) If $\alpha + \beta \in \Phi$ and $g \in P(\alpha, 0) \cap P(\alpha + \beta, 0)$ then
 $x_\beta(b) \cdot S_\alpha(a, g) x_{\beta}(-b)\in P(\alpha, 0).$
\end{enumerate}

Some implication: suppose $g \in P(\alpha, 0)$, then $g x_{-\alpha}(mX) \in P(\alpha, m)$ by the definition of the latter.
\begin{multline}S(\alpha, g \cdot x_{-\alpha}(mX)) = x_\alpha(aX^{-1})\cdot g \cdot x_{-\alpha}(mX) \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha = \\
= S(\alpha, g) \cdot x_\alpha(aX^{-1}) \cdot x_{-\alpha}(mX) \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha % = \\
%= S(\alpha, g) \cdot x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am) \cdot x_{\alpha}\left(\frac{aX^{-1}}{1+am}\right) \cdot \{1+am, X\} \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha = \\
= S(\alpha, g) \cdot x_{-\alpha}\left(\frac{mX}{1+am}\right) \cdot \langle -a, m\rangle_\alpha \cdot h_\alpha(1+am). 
\end{multline}

Let us show that F3 and F4 hold automatically.
Suppose $\alpha \perp \beta$, $g \in P(\alpha, m) \cap P(\beta, m')$, then $g = g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X)$, where 
$g_0 \in P(\alpha, 0) \cap P(\beta, 0)$ (here we use the fact that $P(\alpha, 0)$ (resp. $P(\beta, 0)$) is a subgroup containing $x_{-\beta}(mX)$ (resp. $x_{-\alpha}(m'X)$)).
Then 
\[ S_\alpha(a, g) = x_\alpha(aX^{-1})\cdot g_0 \cdot x_{-\alpha}(mX) \cdot x_{-\beta}(m'X) \cdot x_\alpha\left(-\frac{aX^{-1}}{1 + am}\right) \cdot \{X, 1+ am\}_\alpha
  = S_\alpha(a, g_0 \cdot x_{-\alpha}(mX)) \cdot x_{-\beta}(m'X).\]
We need to show $S_\alpha(a, g_0 \cdot x_{-\alpha}(mX)) \in P(\beta, 0)$ but this is obvious since the latter is a subgroup.
\end{comment}
\begin{align*} {}^{x_\gamma(X^{-1})}x_\alpha(bX^{-1}) = {}^{x_\gamma(X^{-1})}[x_{-\beta}(b'X^{-1}), x_{\alpha+\beta}(1)] & \text{ by R$2_1$}\\
 = [x_{-\beta}(b'X^{-1}), {}^{x_\gamma(X^{-1})}x_{\alpha+\beta}(1)] & \text{ by R$3_1$ for sharp angles}\\
 = [[x_{-\beta-\gamma}(b''), x_\gamma(X^{-1})], {}^{x_\gamma(X^{-1})}x_{\alpha+\beta}(1)] & \text{ by R$2_1$}\\
 = [x_{-\beta-\gamma}(b''), [x_\gamma(X^{-1}), x_{\alpha+\beta}(1)]] & \text{ by R$3_0$}\\
 = x_{\alpha}(b'''X^{-1}) & \text{ by R$2_1$.} \end{align*}

\begin{align*} x_{\alpha+\beta+\gamma}(abX^{-1}) = {}^{x_{-\beta}(X^{-1})}\!x_{\alpha+\beta+\gamma}(abX^{-1}) & \text{ by the above relation}\\
 = {}^{x_{-\beta}(X^{-1})}\![x_{\alpha+\beta}(b'), x_\gamma(aX^{-1})] & \text{ by R$2_1$} \\
 = [x_{\alpha}(b'X^{-1}) x_{\alpha+\beta}(b'), x_\gamma(aX^{-1})] & \text{ by R$2_1$ and R$3_1$ for sharp angles }\\
 = {}^{x_{\alpha}(b'X^{-1})}\!x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$2_1$} \\
 = x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$3_1$ for sharp angles.} \end{align*}

\printbibliography
\end{document}

>>>>

\documentclass[oneside, 8pt]{amsart}
\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
\usepackage[breaklinks=true,unicode]{hyperref}
\usepackage[hyperref=true, backend=biber, bibencoding=utf8, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
\usepackage[capitalize]{cleveref}
\usepackage[matrix,arrow,curve]{xy}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage[notref,notcite]{showkeys}

@@

\DeclareMathOperator{\Ker}{Ker}
\DeclareMathOperator{\Img}{Im}
\DeclareMathOperator{\St}{St}
\DeclareMathOperator{\GG}{G}
\DeclareMathOperator{\E}{E}
\DeclareMathOperator{\HH}{H}
\DeclareMathOperator{\K}{K}
\DeclareMathOperator{\GW}{GW}
\DeclareMathOperator{\colim}{colim}
\newcommand{\inv}{^{-1}}

@@

\subsection{Computation of the kernel of the map of evaluation at \texorpdfstring{$0$}{0}.}
For a pair $(R, I)$ we denote by $\overline{\St}(\Phi, R, I)$ the image of the map $\mu$ from~\eqref{relSteinberg-def}, in particular, it is a normal subgroup of $\St(\Phi, R)$.
We also denote by $\St(\Phi, I)$ the subgroup of $\St(\Phi, R)$ generated as a group by root unipotents of level $I$.
It is clear that $\overline{\St}(\Phi, R, I)$ contains $\St(\Phi, I)$ and, in fact, is its normal closure.
We also denote by $\overline{H}(\Phi, R, I)$ the subgroup of $\overline{\St}(\Phi, R, I)$ generated by the semisimple root elements $h_\alpha(u)$ and symbols $\{u, v\}$, $u \in (1+I)^*$, $v \in R^*$, $\alpha\in \Phi$.

@@

\subsection{The subgroups \texorpdfstring{$P_\alpha(0)$}{Pa(0)}, \texorpdfstring{$P_\alpha(*)$}{Pa(*)} and their properties.} 
For a root system $\Phi$ consider the following subsets of $\Phi$:
\begin{align} Z_+(\alpha) & = \{ \beta \in \Phi \mid \langle \alpha, \beta \rangle > 0 \}, \\
   Z_0(\alpha) & = \{ \beta \in \Phi \mid \alpha + \beta \not\in \Phi,\ \langle \alpha, \beta \rangle = 0 \}, \\
   Z(\alpha)   & = Z_0(\alpha) \sqcup Z_+(\alpha). \end{align} 
Clearly, $Z_0(\alpha)$ (resp. $Z_+(\alpha)$) is a reductive (resp. special) subset of $\Phi$.

@@

For the rest of this subsection $\Phi$ is a simply-laced root system of rank $\geq 3$ and $\alpha$ is a root of $\Phi$. Notice that in the simply-laced case the assumption $\alpha+\beta\not\in \Phi$ in the definition of $Z_0(\alpha)$ is superfluous, i.\,e. $Z_0(\alpha) = \{ \alpha\in\Phi \mid \alpha \perp \beta \}$
(cf.~\cite[Proposition~5.7]{St71}).

@@

\subsection{The subgroups \texorpdfstring{$K(\alpha, \beta)$}{K(a,b)} and their properties}
Throughout this subsection $\alpha, \beta$ denote a fixed pair of roots of $\Phi$ forming a sharp angle (i.\,e. $\langle \alpha, \beta \rangle = 1$). We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
\begin{df} Denote by $K(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the following elements:
 \begin{enumerate}
  \item $z_\gamma(Xf, \xi)$, for all $\gamma \in \Phi \setminus \Psi$;
  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$;
  \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
  \item $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$. \end{enumerate} \end{df}

@@

\begin{comment}
The next step of the proof is to pass from the set $V_0'$ to its quotient $V_0$ 
We allow multiplying the second component on the right by an element of $\mathrm{im}(\St(\Phi, A, M) \to \St(\Phi, A))$
 (this operation is well defined for $V'_0$).

\begin{multline}
 T_\alpha(bX^{-1}) T_\alpha(aX^{-1}) \left(g,\ h,\ u\right) \sim \\ \sim
T_\alpha(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am),\ u(1 + am)\right) = \\
 = \left( x_\alpha\left((a+b)X^{-1}\right)\cdot g,\ h',\ u(1 + am + bm) \right) \sim T_\alpha((a+b)X^{-1}) \left( g,\ h,\ u\right),\text{ since} \end{multline} 
 \begin{multline}
h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot h^{-1}_\alpha(1+am) \cdot x_\alpha\left(-\tfrac{bX^{-1}}{1 + \tfrac{bm}{1+am}}\right) = \\ = 
 h \cdot x_\alpha\left(- \tfrac{aX^{-1}}{1 + am} - \tfrac{bX^{-1}}{(1+am)(1 + am + bm)}\right) \cdot h^{-1}_\alpha(1+am) \sim  
  h \cdot x_\alpha\left(- \tfrac{(a+b)X^{-1}}{1 + am + bm}\right).
\end{multline}

If $\alpha + \beta \not \in \Phi$ but $\alpha - \beta \in \Phi$, $\pi(g, h, u) \in P(\alpha, m) \cap P(\beta, m')$ then
$S_\alpha(a, \pi(g, h, u))\cdot  h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \in P(\beta, \tfrac{m'}{1 + am})$
%($\beta = 2r$, $\alpha = 1r$, $\gamma = 12$, $\gamma = \alpha - \beta$)
\begin{multline}
 T_\beta(bX^{-1}) T_\alpha(aX^{-1}) \left(g, h, u\right) = 
 T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) ,\ u(1 + am)\right) \sim \\ 
 \sim T_\beta(bX^{-1}) \left(x_\alpha(aX^{-1})\cdot g,\ h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-m'a),\ u(1 + am)\right) = \\
 = (x_\beta(bX^{-1}) x_\alpha(aX^{-1}) \cdot g, h', u(1 + am + bm')), \text{ where} \end{multline} 
 \begin{multline}
 h' = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha-\beta}(-N_{\alpha-\beta, \beta}m'a) \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) \sim \\
    \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am}\right) \cdot h^{-1}_\alpha(1 + am) \cdot x_{\alpha}\left(\tfrac{m'abX^{-1}(1+am)}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)}{1 + am + bm'}\right) = \\
 = h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am} + \tfrac{m'abX^{-1}}{(1+am)(1 + am + bm')}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}(1+am)^{1 -\langle \beta, \alpha \rangle}}{1 + am + bm'}\right) \cdot h^{-1}_\alpha(1 + am) \sim \\
 \sim h \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1 + am + bm'}\right) \cdot x_\beta\left(-\tfrac{bX^{-1}}{1 + am + bm'}\right).
\end{multline}
The latter expression is symmetric.

\begin{align*} {}^{x_\gamma(X^{-1})}x_\alpha(bX^{-1}) = {}^{x_\gamma(X^{-1})}[x_{-\beta}(b'X^{-1}), x_{\alpha+\beta}(1)] & \text{ by R$2_1$}\\
 = [x_{-\beta}(b'X^{-1}), {}^{x_\gamma(X^{-1})}x_{\alpha+\beta}(1)] & \text{ by R$3_1$ for sharp angles}\\
 = [[x_{-\beta-\gamma}(b''), x_\gamma(X^{-1})], {}^{x_\gamma(X^{-1})}x_{\alpha+\beta}(1)] & \text{ by R$2_1$}\\
 = [x_{-\beta-\gamma}(b''), [x_\gamma(X^{-1}), x_{\alpha+\beta}(1)]] & \text{ by R$3_0$}\\
 = x_{\alpha}(b'''X^{-1}) & \text{ by R$2_1$.} \end{align*}

\begin{align*} x_{\alpha+\beta+\gamma}(abX^{-1}) = {}^{x_{-\beta}(X^{-1})}\!x_{\alpha+\beta+\gamma}(abX^{-1}) & \text{ by the above relation}\\
 = {}^{x_{-\beta}(X^{-1})}\![x_{\alpha+\beta}(b'), x_\gamma(aX^{-1})] & \text{ by R$2_1$} \\
 = [x_{\alpha}(b'X^{-1}) x_{\alpha+\beta}(b'), x_\gamma(aX^{-1})] & \text{ by R$2_1$ and R$3_1$ for sharp angles }\\
 = {}^{x_{\alpha}(b'X^{-1})}\!x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$2_1$} \\
 = x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$3_1$ for sharp angles.} \end{align*}
\end{comment}
\printbibliography
\end{document}
